``Interestingness'' in Mathematical Theory Exploration

### 2019-11-24 PhDThesis/clustering.tex
More citations

fibTail n = helperFib n 0 1
  \end{haskell}
  \caption{Haskell equivalents of the Common Lisp functions in Figure \ref{fig:lisp}.}
  \label{fig:haskelllisp}
\end{figure}

\begin{figure}
  \centering
    \tikzstyle{block} = [rectangle, draw]
    \tikzstyle{line}  = [draw, -latex']
    \begin{tikzpicture}[node distance=3cm]
      \node [block] (c1) {
        \begin{tikzpicture}[node distance = 1cm]
          \node [block]                    (factTail)  {\hs{factTail}};
          \node [block, below of=factTail] (fibTail)   {\hs{fibTail}};
          \node [block, below of=fibTail]  (powerTail) {\hs{powerTail}};
        \end{tikzpicture}
      };
      \node [block, right of=c1] (c2) {
        \begin{tikzpicture}[node distance = 1cm]
          \node [block]                (fact)       {\hs{fact}};
          \node [block, below of=fact] (helperFact) {\hs{helperFact}};
        \end{tikzpicture}
      };
      \node [block, right of=c2] (c3) {
        \begin{tikzpicture}[node distance = 1cm]
          \node [block]                       (fib)         {\hs{fib}};
          \node [block, below of=fib]         (helperFib)   {\hs{helperFib}};
          \node [block, below of=helperFib]   (helperPower) {\hs{helperPower}};
          \node [block, below of=helperPower] (power)       {\hs{power}};
        \end{tikzpicture}
      };
  \end{tikzpicture}
  \caption{Typical clusters for the functions in Figure \ref{fig:haskelllisp}.}
  \label{fig:haskellcluster}
\end{figure}

>>>>

fibTail n = helperFib n 0 1
  \end{haskell}
  \caption{Haskell equivalents of the Common Lisp functions in
    Figure~\ref{fig:clusterlisp}.}
  \label{fig:clusterhaskelllisp}
\end{figure}

\begin{figure}
  \centering
    \tikzstyle{block} = [rectangle, draw]
    \tikzstyle{line}  = [draw, -latex']
    \begin{tikzpicture}[node distance=3cm]
      \node [block] (c1) {
        \begin{tikzpicture}[node distance = 1cm]
          \node [block]                    (factTail)  {\hs{factTail}};
          \node [block, below of=factTail] (fibTail)   {\hs{fibTail}};
          \node [block, below of=fibTail]  (powerTail) {\hs{powerTail}};
        \end{tikzpicture}
      };
      \node [block, right of=c1] (c2) {
        \begin{tikzpicture}[node distance = 1cm]
          \node [block]                (fact)       {\hs{fact}};
          \node [block, below of=fact] (helperFact) {\hs{helperFact}};
        \end{tikzpicture}
      };
      \node [block, right of=c2] (c3) {
        \begin{tikzpicture}[node distance = 1cm]
          \node [block]                       (fib)         {\hs{fib}};
          \node [block, below of=fib]         (helperFib)   {\hs{helperFib}};
          \node [block, below of=helperFib]   (helperPower) {\hs{helperPower}};
          \node [block, below of=helperPower] (power)       {\hs{power}};
        \end{tikzpicture}
      };
  \end{tikzpicture}
  \caption{Typical clusters for the functions in
    Figure~\ref{fig:clusterhaskelllisp}.}
  \label{fig:haskellcluster}
\end{figure}

### 2019-11-24 PhDThesis/futurework.tex
Remove dupe label
More citations

\subsubsection{Interestingness}
\label{sec:interestingness}

@@

Since tools like \hipspec{} already call out to third-party automated theorem
provers, and indeed our own \mlforhs{} system uses the external Weka program, there
may also be merit in using external concept formation or conjecture generation
tools (or reimplementations of their ideas), in order to build up more structure
on top of that provided by the code we are exploring. For example, the
approaches taken by AM \cite{lenat1977automated, lenat1979automated}, Graffiti
\cite{delavina2005some, delavina2005graffiti} and HR
\cite{colton1999automatic, colton2000agent} could be used alongside those of
\quickspec{}.

>>>>

\subsubsection{Interestingness}

@@

Since tools like \hipspec{} already call out to third-party automated theorem
provers, there may also be merit in using external concept formation or
conjecture generation tools (or reimplementations of their ideas), in order to
build up more structure on top of that provided by the code we are exploring.
For example, the approaches taken by
AM~\cite{lenat1977automated, lenat1979automated},
Graffiti~\cite{delavina2005some, delavina2005graffiti} and
HR~\cite{colton1999automatic, colton2000agent} could be used alongside those of
\quickspec{}.

### 2019-11-24 PhDThesis/litreview_machinelearning.tex
More citations

\section{Machine Learning Applications in Mathematics, Logic and Programming
  Language Theory}

Machine Learning (ML) applies statistical techniques to find patterns in data.
ML algorithms are numerical in nature, and often rely on assumptions such as
continuity and differentiability. In contrast, the worlds of mathematical
formulae, formal logic and computer programs are usually discrete and symbolic.
This makes application of ML to these domains more difficult than, say, image
processing. This difficulty is clear from attempts to train Artificial Neural
Networks to evaluate snippets of program code~\cite{zaremba2014learning}: even
with heavily restricted inputs (e.g. short integer calculations, with little
nesting, requiring only linear time and memory use, and evaluating with
``teacher forcing'' to prevent errors accumulating) the accuracy quickly drops
with program length. Coupled with the success of \emph{deep learning} (efficient
back-propagation/credit-assignment over many differentiable processing steps)
compared to prior hand-engineered AI solutions, it is apparent that symbolic
and statistical methods are \emph{complementary}; hence the need to identify
relevant sub-tasks for each technique when combined into some larger system.

>>>>

\section{Machine Learning Applications to Formal Systems}

Machine Learning (ML) applies statistical techniques to find patterns in data.
ML algorithms are numerical in nature, and often rely on assumptions such as
continuity and differentiability. In contrast, formal systems such as
mathematical formulae, formal logic and computer programs are usually discrete
and symbolic. This makes application of ML to these domains more difficult than,
say, image processing, which has a natural representation as numeric pixel
values. This difficulty is clear from attempts to train Artificial Neural
Networks (ANNs) to evaluate snippets of program code~\cite{zaremba2014learning}:
even with heavily restricted inputs (e.g. short integer calculations, with
little nesting, requiring only linear time and memory use, and evaluating with
``teacher forcing'' to prevent errors accumulating) the accuracy quickly drops
with program length. Coupled with the success of \emph{deep learning} (efficient
back-propagation/credit-assignment over many differentiable processing steps)
compared to prior hand-engineered AI solutions, it is apparent that symbolic
and statistical methods are \emph{complementary}; hence the need to identify
relevant sub-tasks for each technique when combined into some larger system.
